### 2012-09-11 inst/examples/debug_uniform.Rmd
Analytic multiple noise, for farm run (figure3.Rmd)

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 200
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
````

@@

@@

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = 0.5, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r runall}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], all_low = low$D[,1],
               growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 
               id = "stock")

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
sigma_m <- .5
sigma_i <- .5
````

@@

```{r }
int_f <- function(f, x, q, sigma_m, sigma_i, pars){
  g <- function(X) f(X[1], X[2], pars)
  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
  upper <- c(x + sigma_m, q + sigma_i)
  out <- adaptIntegrate(g, lower, upper)
  out$integral
}

F <- function(x,q, m, n, pars){
  K <- pars[2]
  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
  max(out,0)
}
```

```{r }
require(cubature)
# Confirm that these give the same value, and time performance
system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
```

```{r }
sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=sigma_m, sigma_i=sigma_i, F)
```

```{r }
uniform <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

@@

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
     }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

```{r}
  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), 
               id = "stock")

### 2012-09-11 inst/examples/figure3.Rmd
Analytic multiple noise, for farm run (figure3.Rmd)

We use Monte Carlo integration over the noise processes to determine the transition matrix.

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

``` {r policyscenarios}
scenario <- function(policy_g, policy_m, policy_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

Determine the policies for each of the scenarios (noise combinations).

``` {r runall}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

>>>>

--We use Monte Carlo integration over the noise processes to determine the transition matrix.--

We compute the transition probability analytically, (confirm that this is correct!)

$F(x,q) = \frac{1}{4\sigma_i\sigma_m} \int_{q-\sigma_i}^{q+\sigma_i} dh \int_{x-\sigma_m}^{x+\sigma_m} f(y, h)$

We will use the analytic solution

```{r}
F <- function(x,q, m, n, pars){
  K <- pars[2]
  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
  max(out,0)
}
```

We can verify our solution is the same as the numerical integral (which is slower to compute)

```{r }
int_f <- function(f, x, q, sigma_m, sigma_i, pars){
  g <- function(X) f(X[1], X[2], pars)
  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
  upper <- c(x + sigma_m, q + sigma_i)
  out <- adaptIntegrate(g, lower, upper)
  out$integral
}
```

```{r }
require(cubature)
# Confirm that these give the same value, and time performance
system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
```

``` {r beparallel, cache=FALSE, eval=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

The policies

```{r}
stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0, sigma_i=0, F)
g <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0.5, sigma_i=0, F)
m <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0, sigma_i=0.5, F)
i <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.1, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0.1, sigma_i=0.1, F)
low <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

``` {r policyscenarios, eval=FALSE, include=FALSE} 
# not run
scenario <- function(policy_g, policy_m, policy_i){ 
  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r runall, eval=FALSE, include=FALSE}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````
